### 2019-10-23 tikz/figs/comp_fir_ligo_hinf.tex
Update path to data

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.60\fheight,
    at={(0.0\fwidth, 0.35\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.001,
    xmax=1,
    xtick={0.001,0.01,0.1,1},
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.002,
    ymax=5,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    legend style={at={(1,0)}, outer sep=2pt, anchor=south east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}}
    ]
    \addplot [color=mycolor1, line width=1.5pt]
      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addlegendentry{$H_H(s)$ - $\mathcal{H}_\infty$}
    \addplot [color=mycolor1, dashed, line width=1.5pt]
      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
    \addlegendentry{$H_H(s)$ - FIR}
    \addplot [color=mycolor2, line width=1.5pt]
      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addlegendentry{$H_L(s)$ - $\mathcal{H}_\infty$}
    \addplot [color=mycolor2, dashed, line width=1.5pt]
      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
    \addlegendentry{$H_L(s)$ - FIR}
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.3\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.001,
    xmax=1,
    xtick={0.001,  0.01,   0.1,     1},
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-180,
    ymax=180,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    ]
    \addplot [color=mycolor1, line width=1.5pt, forget plot]
      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
    \addplot [color=mycolor2, line width=1.5pt, forget plot]
      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_hinf.csv};
    \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/comp_ligo_fir.csv};
  \end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.60\fheight,
    at={(0.0\fwidth, 0.35\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.001,
    xmax=1,
    xtick={0.001,0.01,0.1,1},
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.002,
    ymax=5,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    legend style={at={(1,0)}, outer sep=2pt, anchor=south east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}}
    ]
    \addplot [color=mycolor1, line width=1.5pt]
      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
    \addlegendentry{$H_H(s)$ - $\mathcal{H}_\infty$}
    \addplot [color=mycolor1, dashed, line width=1.5pt]
      table [x=freqs, y=Hhm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
    \addlegendentry{$H_H(s)$ - FIR}
    \addplot [color=mycolor2, line width=1.5pt]
      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
    \addlegendentry{$H_L(s)$ - $\mathcal{H}_\infty$}
    \addplot [color=mycolor2, dashed, line width=1.5pt]
      table [x=freqs, y=Hlm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
    \addlegendentry{$H_L(s)$ - FIR}
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.3\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.001,
    xmax=1,
    xtick={0.001,  0.01,   0.1,     1},
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-180,
    ymax=180,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    ]
    \addplot [color=mycolor1, line width=1.5pt, forget plot]
      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
    \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
      table [x=freqs, y=Hhp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
    \addplot [color=mycolor2, line width=1.5pt, forget plot]
      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_hinf.csv};
    \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
      table [x=freqs, y=Hlp, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matcomp_ligo_fir.csv};
  \end{axis}
\end{tikzpicture}

### 2019-10-23 tikz/figs/hinf_synthesis_results.tex
Update path to data

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.5\fheight,
    at={(0.0\fwidth, 0.5\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=1000,
    xtick={0.1, 1, 10, 100, 1000},
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    ]
    \addplot [color=mycolor1, line width=1.5pt, forget plot]
    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};

    \addplot [color=mycolor2, line width=1.5pt, forget plot]
    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};

    \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_weights.csv};

    \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_weights.csv};
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.45\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=1000,
    xtick={0.1, 1, 10, 100, 1000},
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-200,
    ymax=200,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    legend style={at={(1,1.1)}, outer sep=2pt , anchor=north east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}},
    ]
    \addlegendimage{color=mycolor1, dashed, line width=1.5pt}
    \addlegendentry{$W_1^{-1}$};
    \addlegendimage{color=mycolor2, dashed, line width=1.5pt}
    \addlegendentry{$W_2^{-1}$};
    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
    \addlegendentry{$H_1$};
    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_filters_results.csv};
    \addlegendentry{$H_2$};
  \end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.5\fheight,
    at={(0.0\fwidth, 0.5\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=1000,
    xtick={0.1, 1, 10, 100, 1000},
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    ]
    \addplot [color=mycolor1, line width=1.5pt, forget plot]
    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};

    \addplot [color=mycolor2, line width=1.5pt, forget plot]
    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};

    \addplot [color=mycolor1, dashed, line width=1.5pt, forget plot]
    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_weights.csv};

    \addplot [color=mycolor2, dashed, line width=1.5pt, forget plot]
    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_weights.csv};
  \end{axis}

  \begin{axis}[%
    width=1.0\fwidth,
    height=0.45\fheight,
    at={(0.0\fwidth, 0.0\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=1000,
    xtick={0.1, 1, 10, 100, 1000},
    xminorticks=true,
    xlabel={Frequency [Hz]},
    ymin=-200,
    ymax=200,
    ytick={-180,  -90,    0,   90,  180},
    ylabel={Phase [deg]},
    xminorgrids,
    legend style={at={(1,1.1)}, outer sep=2pt , anchor=north east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}},
    ]
    \addlegendimage{color=mycolor1, dashed, line width=1.5pt}
    \addlegendentry{$W_1^{-1}$};
    \addlegendimage{color=mycolor2, dashed, line width=1.5pt}
    \addlegendentry{$W_2^{-1}$};
    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};
    \addlegendentry{$H_1$};
    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_filters_results.csv};
    \addlegendentry{$H_2$};
  \end{axis}
\end{tikzpicture}

### 2019-10-23 tikz/figs/hinf_three_synthesis_results.tex
Update path to data

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.55\fheight,
    at={(0.0\fwidth, 0.45\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=100,
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    legend columns=2,
    legend style={
      /tikz/column 2/.style={
        column sep=5pt,
      },
      at={(1,0)}, outer sep=2pt , anchor=south east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}
    },
    ]
    \addplot [color=mycolor1, dashed, line width=1.5pt]
    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
    \addlegendentry{${W_1}^{-1}$};
    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
    \addlegendentry{$H_1$};

    \addplot [color=mycolor2, dashed, line width=1.5pt]
    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
    \addlegendentry{${W_2}^{-1}$};
    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
    \addlegendentry{$H_2$};

    \addplot [color=mycolor3, dashed, line width=1.5pt]
    table [x=freqs, y=W3, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_weights.csv};
    \addlegendentry{${W_3}^{-1}$};
    \addplot [color=mycolor3, line width=1.5pt]
    table [x=freqs, y=H3, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
    \addlegendentry{$H_3$};
  \end{axis}

@@

    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};

    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};

    \addplot [color=mycolor3, line width=1.5pt]
    table [x=freqs, y=H3p, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/hinf_three_results.csv};
  \end{axis}
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \begin{axis}[%
    width=1.0\fwidth,
    height=0.55\fheight,
    at={(0.0\fwidth, 0.45\fheight)},
    scale only axis,
    xmode=log,
    xmin=0.1,
    xmax=100,
    xticklabels={{}},
    xminorticks=true,
    ymode=log,
    ymin=0.0005,
    ymax=20,
    ytick={0.001, 0.01, 0.1, 1, 10},
    yminorticks=true,
    ylabel={Magnitude},
    xminorgrids,
    yminorgrids,
    legend columns=2,
    legend style={
      /tikz/column 2/.style={
        column sep=5pt,
      },
      at={(1,0)}, outer sep=2pt , anchor=south east, legend cell align=left, align=left, draw=black, nodes={scale=0.7, transform shape}
    },
    ]
    \addplot [color=mycolor1, dashed, line width=1.5pt]
    table [x=freqs, y=W1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_weights.csv};
    \addlegendentry{${W_1}^{-1}$};
    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
    \addlegendentry{$H_1$};

    \addplot [color=mycolor2, dashed, line width=1.5pt]
    table [x=freqs, y=W2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_weights.csv};
    \addlegendentry{${W_2}^{-1}$};
    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
    \addlegendentry{$H_2$};

    \addplot [color=mycolor3, dashed, line width=1.5pt]
    table [x=freqs, y=W3, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_weights.csv};
    \addlegendentry{${W_3}^{-1}$};
    \addplot [color=mycolor3, line width=1.5pt]
    table [x=freqs, y=H3, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
    \addlegendentry{$H_3$};
  \end{axis}

@@

    \addplot [color=mycolor1, line width=1.5pt]
    table [x=freqs, y=H1p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};

    \addplot [color=mycolor2, line width=1.5pt]
    table [x=freqs, y=H2p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};

    \addplot [color=mycolor3, line width=1.5pt]
    table [x=freqs, y=H3p, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/mathinf_three_results.csv};
  \end{axis}
\end{tikzpicture}

### 2019-10-23 tikz/figs/ligo_weights.tex
Update path to data

    \addplot [color=mycolor1, line width=1.5pt]
      table [x=freqs, y=wHm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/ligo_weights.csv};
    \addlegendentry{$|w_H|^{-1}$}

    \addplot [color=mycolor2, line width=1.5pt]
      table [x=freqs, y=wLm, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/ligo_weights.csv};
    \addlegendentry{$|w_L|^{-1}$}

>>>>

    \addplot [color=mycolor1, line width=1.5pt]
      table [x=freqs, y=wHm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matligo_weights.csv};
    \addlegendentry{$|w_H|^{-1}$}

    \addplot [color=mycolor2, line width=1.5pt]
      table [x=freqs, y=wLm, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matligo_weights.csv};
    \addlegendentry{$|w_L|^{-1}$}

### 2019-10-23 tikz/figs/weight_formula.tex
Update path to data

    \addplot [color=black, line width=1.5pt, forget plot]
    table [x=freqs, y=ampl, col sep=comma] {/home/thomas/Cloud/These/Papers/dehaeze19_desig_compl_filte/matlab/mat/weight_formula.csv};

>>>>

    \addplot [color=black, line width=1.5pt, forget plot]
    table [x=freqs, y=ampl, col sep=comma] {/home/thomas/Cloud/thesis/papers/dehaeze19_desig_compl_filte/matlab/matweight_formula.csv};
